# Rcpp
```{r, echo=FALSE}
library(Rcpp)
```
### input data type and function
<ul>
  <li>int
  <li>double
  <li>std::string	
  <li>bool
  <li>IntegerVector
  <ul>
    <li> list.size : 同length(list)
  </ul>
  <li>NumercicVector
  <li>LogicalVector
  <li>CharacterVector
  <li>GenericVector
  <li>ExpressionVector
  <li>RawVector
  <li>IntergerMatrix
  <ul>
    <li> NumericMatrix x(n,m) : 產生nxm的矩陣
    <li> x.nrow(), x.ncol(), x.size() :確認維度
    <li> x(i,j) : 看xij
    <li> x.row(i) or x(i,_), x.column(j) or x(_,j)
    <li> transpose(x) 轉置
    <li> NumericMatrix::zeros(n), NumericMatrix::eye(n) : 建立n階的0或單位方陣
  </ul>
  <li>NumericMatrix
</ul>

### Rcpp調用Rmath.h函數
double  expm1(double); /* = exp(x)-1 {care for small x} */

double  log1p(double); /* = log(1+x) {care for small x} */

double	beta(double, double);
double	lbeta(double, double);

double	choose(double, double);
double	lchoose(double, double);

### 架構
#### Add
```{r}
cppFunction('int cpp_add(int x, int y, int z) {
  int sum = x + y + z;
  return sum;
}')
cpp_add(1,2,3)

cppFunction('double cpp_sum(NumericVector x) {
  int n = x.size();
  double total = 0;
  for(int i = 0; i < n; ++i) {
    total += x[i];
  }
  return total;
}')
cpp_sum(c(1,2,3))
```
#### Sort
```{r}
cppFunction('NumericVector cpp_sort(NumericVector x) {
  int x_length = x.size();
  for(int i = 0; i < x_length-1; ++i) {
    for(int j = 0; j < x_length-1-i; ++j) {
      if (x[j] > x[j+1]) {
        double tmp = x[j];
        x[j] = x[j+1];
        x[j+1] = tmp;
      }
    }
  }
  return x;
}')

library(microbenchmark)
x <- runif(100)
x.benchmark <- microbenchmark(
  sort(x),
  cpp_sort(x)
)
x.benchmark
```
#### Row sum
```{r}
cppFunction('NumericVector rowSumsC(NumericMatrix x) {
  int nrow = x.nrow(), ncol = x.ncol();
  NumericVector result(nrow);
  for (int i = 0; i < nrow; i++) {
    double total = 0;
    for (int j = 0; j < ncol; j++) {
      total += x(i, j);
    }
    result[i] = total;
  }
  return result;
}')

x <- matrix(sample(100), 10)
x.benchmark <- microbenchmark(
  rowSums(x),
  rowSumsC(x)
)
x.benchmark
```
### 載入函數
可以寫一個cpp_sum.cpp的檔案
```
#include <Rcpp.h>
using namespace Rcpp;

// [[Rcpp::export]]
double cpp_sum(NumericVector x) {
  int n = x.size();
  double total = 0;
  for(int i = 0; i < n; ++i) {
    total += x[i];
  }
  return total;
}
```
並在R裡接通
```
sourceCpp("cpp_sum.cpp")
cpp_sum(c(1,2,3))
```
或是在R裡直接
```{r}
sourceCpp(code='
#include <Rcpp.h>
using namespace Rcpp;
// [[Rcpp::export]]
double cpp_sum(NumericVector x) {
  int n = x.size();
  double total = 0;
  for(int i = 0; i < n; ++i) {
    total += x[i];
  }
  return total;
}
')
cpp_sum(c(1,2,3))
```